Gap formation and stability in non-isothermal protoplanetary discs

### 2015-03-26 paper/results.tex
Response 2

{\bf For completeness we also simulated a locally
  isothermal disk (at lower resolution) with $\epsilon=0.05$ where the
  sound-speed is kept strictly equal to its initial value.  This
  simulation yield a most unstable growth rate
  $\sigma/\Omega(r_p)\simeq 0.05$ at $m=5$,   
  compared with a value of $0.085$ at $m=?$ for a corresponding
  simulation that includes the energy equation but with rapid cooling
  $\tilde{\beta}=0.01$. However, the vortex evolution is similar.}

>>>>

{\bf For completeness we also simulated a locally
  isothermal disk with $\epsilon=0.05$ where the
  sound-speed is kept strictly equal to its initial value.  This
  simulation yield a most unstable growth rate
  $\sigma/\Omega(r_p)\simeq 0.05$ at $m=5$,   
  compared with a value of $0.085$ at $m=6$ for a corresponding
  simulation that includes the energy equation but with rapid cooling
  $\tilde{\beta}=0.01$. However, the vortex evolution is similar.}
